Toward dynamic models of combat or lack thereof in animal mating

### 2016-01-25 ms.tex
fixed remake issue in importer, added some event hoppping theory stuff

The area that a male $m$ with speed trait $v$ and radius trait $r$ can search in time step $dt$ is
\begin{equation}
    A_{searched} = 2r \cdot v \cdot dt
\end{equation}
See Fig. \ref{fig:area searched}.

@@

The probability of a male that covers $A_{searched}$ area in time period $dt$ encountering any nest is:
\begin{equation}
    P(\rm {discovery}) = \frac {N \cdot A_{searched}} {A_{total}}
\end{equation}
\citep{Gillespie-1976}
The energy used by a male with speed $v$ and radius $r$ is 
\begin{equation}
    E(r,v) = k_{search} \cdot r \cdot v
\end{equation}
where $k_{search}$ is a constant.

>>>>

The area that a male $m$ with speed trait $v$ and radius trait $r$ can search in one time step is
\begin{equation}
    2r \cdot v
\end{equation}
See Fig. \ref{fig:area searched}.

@@

The probability of a male that covers $A_{searched}$ in one time step encountering any nest is:
\begin{equation}
    P(\rm {discovery}) = \frac {N \cdot 2r\cdot v} {A_{total}}
\end{equation}
Let $t_{mat}$ be the time when a male matures.
Now the maximum time possible time that a male can spend searching is $t_{max} = t_{females mature} - t_{mat}$

The expected number of events is $$ P( \rm {discovery}) \cdot t_{max}$$.
We then use this as the $\lambda$ parameter to draw the number of nest discovery events for this individual $n$ from the poisson distribution.

We then pull $n$ numbers from the uniform distrobution with lower bound $t_{mat}$ and upper bound $t_{females mature}$ as the times of these discovery events.

%I think I might use a priority queue for this...

\citep{Gillespie-1976}
The energy used by a male with speed $v$ and radius $r$ is 
\begin{equation}
    E(r,v) = k_{search} \cdot r \cdot v
\end{equation}
where $k_{search}$ is a constant.
